\chapter{Introduction} \label{chap:intro}

%\version{v1.11.2015}

\section*{}
\section{Project Background/Overview}
As time goes on, population of world increases and that population needs a roof over their head and places to work at. That requires more infrastructure to be constructed. To cater that growth, real estate comes in to play. One company could be managing thousands of different real estate projects and they need a central platform to do such tasks for both the clients and owners of those projects. Here Estate+, the proposed project, leads a helping hand with its cross-platform ability to cater all types of users.
\section{Problem Description}
Managing numerous real estate projects requires extreme amount of time and work dedication. A lot of paper work is involved and meetings with clients is day to day basis. If a client needs to get in contact with the owner, they need to contact the owner's managers who then schedule a meeting. Also to follow up their investments through the project's life span, client has to go through a hectic routine of processes to do so. Moreover, new projects in development which require investments from different clients is needed. It could be hard to reach potential clients who are looking for investments and have no knowledge of the correct process. Having a central platform which provides solutions to all the above issues would be a great helping hand.
\section{Project Objectives}
To cater the problems described in previous section, a cross-platform application is developed which can run on Web, Android and iOS. The mobile version of the application is where all the clients and owners of real estate projects are targeted. However, the web will be accessible to authorized personal by the Owner such as Managers and CROs.
\section{Project Scope}
Clients can view the projects that are for sale, looking for investments etc. They can also track their payment records that are involved in a specific project. Client will also have the ability to submit their payment to the owner through the application which will be recorded in a database. Moreover, to cater customer services, client will be able to schedule meetings with the owner through the app and chat with Customer Relations Officer as well.\\
Owners will interact with the application through mobile as well. They will have their dashboard on the phone which shows all the projects they own and payments involved in those projects. They will also have the ability to create Admin accounts for their managers which can be used to manage their business.\\
Managers of the owners will have access to the application on the Web Portal. They will be able to see all the projects created by their Owner and the transactions involved in them. All the scheduled meetings with the owner will be displayed on the web portal which will be first approved by the manager. Manager will also be able to create accounts for CROs which will be used for customer services purposes.\\
CROs will have all their chats with customers displayed on the web portal to communicate with the customers
