\chapter{Conclusions}\label{chap:conclusions}
%\version{v1.10.2015}

\section*{}
The excessive creation of multiple screens for both Web and Mobile led to a small introduction towards industry level projects. Since a screen consisted of more than 1 component, it showed places where it is best to use State-full and State-less components. The data also got shared between multiple screens without navigation which introduced the concept of Contexts in React. Different form of navigation in React and React Native were also discovered such as Bottom Tabs, Drawer, Router etc. Minor implementation of animations in React Native introduced Reanimated. How Data is stored locally on phone using AsyncStorage in React Native was also a great learning experience. \\
Creation of personal API and Server was also learned during the development of this project. Postman was used to test the personal Server which was also a new addition to the skill set. It showed how to connect PostgreSQL with the server through pools provided by the pg module. Different SQL queries introduced to different database concepts such as Joins, Where, Group etc. It also show cased how to connect any database with IntelliJ DataGrip which is a great software for database testing and management. \\
The whole process opened so many doors towards different tools and technologies that are being practiced and implemented in the real world. It also showed the best ways to implement them and the standards that are being followed to do it. These new learned skills will be a great helping hand while entering the industry.
